\section{Chapter 3}
\subsection{Methodology}

\subsubsection{The purpose of the research}
The aim of the research is to investigate innovation within schools in the UAE. There will be a focus on the understanding of innovation itself, something that has come out of the literature review and preliminary research. An additional areas of focus is the reaction, if any, from schools to the introduction of innovation as an inspection. Finally, some schools, if applicable, will be chosen to look at any innovative practice occurring. The aim being to produce a summary or reduction of best practice for innovation in schools.

\subsubsection{The nature of the knowledge which is created}

\subsubsection{Types of research}

As the research is multifaceted, it is obviously important to employ different types of research methods to ascertain the best method for data collection in each instance. In the first instance, the seminal \textit{Research Methods in Education} by \citet{Cohen2005} is the starting point to identify possible research methods that might be suitable for each task.

In simple terms, the research aims to study the effect of an external influence (the innovative drive) on schools. The research methodology options are therefore already narrowed; the change has already happened and therefore does not need to be discovered or inferred. This strongly rules out the \textit{ex post facto} methodology as the cause is already known to us.

Naturalistic enquiry was also included as a possible research method, as the "intention of the research is to create as vivid a reconstruction as possible of the culture or groups being studied", \cite{Cohen2005} which is not not only a possibility, but a good method of finding out the current impact of the changes. There are several elements of a naturalistic enquiry which seem to suggest it would be a good fit. Cohen states that typically, "researchers do not know in advance what they will see or what they will look for" \cite{Cohen2005} which given the area is new in UAE (and as a focus, world wide), there is no obvious starting point. Cohen follows by saying that "research designs emerge over time" and that "social research should be conducted in natual, uncontrived, real world settings with as little intrusiveness as possible by the researcher". On the subject of this method, he goes on to say: "data [is] analysed inductively, with constructs deriving from the data during the research". This idea of inductive, or iterative investigation, which constitutes adapting and evolving the research as new data emerges, is one that is very close the anticipated model as no-one knows what changes have happened and how people are perceiving them. 

The concern with naturalistic enquiry would be the lack of structure; while it seems a good fit, there is a danger that if the research designs emerging were weak, the inductive approach might break down and lead to weak research.

Surveys were another possible approach as they "set out to describe and to interpret \textit{what is}." \cite[p. 169]{Cohen2005} As the impact of the changes are unknown, describing the current state of those changes would be a reasonable method. The interpretation was a slight concern given the (anticipated) relatively small sample size and the difficulty in being in a position of strength in order to interpret or draw any strong conclusions from the data.

Action research and experiments, which in the context of education are commonly seen as classroom-based research, were thought to be too narrow and practical for this research context. An action research focus for innovation would look at an area such as the effect of innovative teaching on lessons or students. While a valuable part of the innovation framework, it would have been too narrow to focus solely on the effect in the classroom. Had the innovation focus been more developed, it might have been a useful addition, but it was thought to be too new to be able to make any useful conclusion about classroom practice.

Given the different areas of research, the decision was made to take a pragmatic approach to research which will encompass naturalistic enquiry for discovery of the influence within schools and school culture, and surveys to find out the measurable data within the changes.  A pragmatic approach fits well with this attempt to find the holistic effect of innovation within schools. According to Johnson, pragmatic research "[v]iews current truth, meaning, and knowledge as tentative and as changing over time" \cite[p. 18]{Johnson_2004}. Nowhere more is this important than in the early stages of this innovation drive. As schools digest and develop the changes and inspectors make their first inspections, the understanding of innovation in schools may well change.

Johnson goes on to state that this research method "[e]ndorses eclecticism and pluralism (e.g., different, even conflicting, theories and perspectives can be useful; observation, experience, and experiments are all useful ways to gain an understanding of people and the world)" \cite[p. 18]{Johnson_2004}. It was identified early on that defining innovation and what may constitute it in schools would be an area of focus. Researching the multiplicity of innovation is more useful in this context than discarding data because not everyone may agree on what it is. The conflicting data is in itself a useful data point.


\subsubsection{The reason for your choice of research methodology}

\subsubsection{The nature of the knowledge which is created}
Making innovation a deliberate focus within an education system is something that has never been consciously attempted before. By researching this area, the knowledge created will usable to decide to what extent innovation is beneficial in schools and how best to achieve an innovative school. The research will be generalisable for a school in the context of using the data from other schools who have been found to be excelling in providing an innovative education. It will also generate knowledge useful in the wider sense of trying to improve a nation's education system through a focus on innovation. 

\subsubsection{The possible measures for trusting the research (validity and reliability)}
While the difficulty in obtaining accuracy in responses due the differing opinions on what innovation in education is, this will not diminish the validity of those responses, in themselves they are valuable data points. 

\subsubsection{The nature and form of what may be generalised from the research.}
The surveys will provide data on how well teachers can currently define innovation. Through the same method, data will be provided which will indicate how many schools have changed in response to the innovation drive. The interviews along with the case studies will provide data on what exactly schools are deeming as innovation as well as what good practice they are doing. TODO: haven't mentioned e.g. surveys yet?

\subsubsection{The power relationships and involvement of stakeholders and the effects that this may have.}

It is important to note of the power dynamic in this ecosystem, one which is crucial to bear in mind when conducting the research, or indeed reading any results or conclusions. The innovation initiative is one that has been proposed and distributed by an external body to schools, a body which schools are otherwise held account to. Anyone participating in this research, especially anyone in a more senior leadership role, will therefore have a tendency to portray an image that may perhaps be more generous that may actually be the case. The responsibility of implementing these changes will fall to senior leaders, so any self-provided evidence of progress or success will need to be validated by multiple parties.

To minimise the effect of exaggeration on successes, the research will be conducted face-to-face where it is thought that a disclaimer or explanation would facilitate more honest dialogue. Additionally, all quantitative research conducted will be confidential, institutions will be anonymised  and independent of institution in order to gain the most accurate data feasible. 

\subsubsection{The ethical basis of the research.}
Given the context of the innovation project, a key issue of ethics is anonymity. The relative level of success of the initiative will depend on a large number of factors, some which may not reflect positively on the staff or schools taking part. Individuals taking part have been guaranteed confidentiality as well as making the schools taking part anonymous. With a range of schools and the nature of innovations such as this, there will inevitably be some results which look less favourable for some schools. It is also important to ground this research in one very specific area which is a small part of inspection framework which means no inferences can be made on the schools in the wider context.
With a range of schools and the nature of innovations such as this, there will inevitably be some results which look less favourable for some schools. It is also important to ground this research in one very specific area, innovation, which means no inferences can be made on the schools in the wider context. If a school is found not to have reacted to the changes, there is no reflection on the quality of the school overall.

\subsubsection{Identify any bias that the researcher may bring to the research and how they intend to overcome this}

The author has made his own biases known in a profession autobiography in this document and discussed the ways to mitigate those.

\subsubsection{Identify any variables and how they can will be dealt with}

\subsection{Methods of Data Collection}
Having selected a pragmatic or mixed methods research methodology, the data collection methods chosen are questionnaires, interviews and observations.

Throughout almost every area of the data collection, one of the key concerns was that teachers, unlike many professions, do not have "free time" during the day. That is, during contact hours, a teacher could not reasonably be expected to answer a phone or reply to an email. Additionally, outside of contact hours, many teachers use that time to plan and assess student work. Teachers' time is therefore relatively costly, and asking them to take time out to provide data altruistically is a huge challenge.
The most constraining element in this area of data collection is the time (and potentially distance) needed to provide any face-to-face data collection for all but questionnaires. Needing to contact as many different people in different schools as possible meant interviews were time-prohibitive, even if they were demoted from in-person to over the phone. Accounts, observations and personal constructs, all required either a prohibitively large period of time from me, or to push the responsibility onto the teachers themselves to produce the data, both not acceptable. By reason of elimination, questionnaires were the only method where many teachers' opinions could be solicited (anticipating a level of non-completion) and the time spent both all parties would be minimised.

The first area of research is finding out data from teachers. This encompasses looking at definitions and examples of innovation, as well as seeing if they believe their school has changed in response to the innovation drive. As we are collecting data about the current situation, it had to be decided to choose from interviews, questionnaires, accounts, observations and personal constructs as possible methods, as taken from \citet{Cohen2005}.

The most constraining element in this area of data collection is the time (and potentially distance) needed to provide any face-to-face data collection for all but questionnaires. Needing to contact as many different people in different schools as possible meant interviews were time-prohibitive, even if they were conducted over the phone. Accounts, observations and personal constructs, all required either a prohibitively large period of time from the researcher, or to push the responsibility onto the teachers themselves to produce the data, both choices were not acceptable. By reason of elimination, questionnaires were the only method where many teachers' opinions could be solicited (anticipating a level of non-completion) and the time spent both all parties would be minimised. 

While the data required from teachers is mostly quantitative, the more open-ended questions allowed for a degree of freedom in expressing their thoughts both on innovation, and to their school's 

There will be three main methods of data collection for the research, a mix of qualitative and quantitative data collection which comprise the chosen pragmatic approach.

\subsubsection{Questionnaires}
Questionnaires will be used to collect the main part of the data due to the nature of data required. The questions of how well understood innovation is, and to what extent it had been implemented by schools are ones that could be answered by teachers. Ideally, interviews would have been conducted in order to establish meaning, inference and to gain clarity. Due to the time constraints mentioned earlier however, questionnaires were chosen as a method which could be easily distributed which would mean the anticipated low interest rate could be mitigated as much as possible with a larger sample size which is simply not feasible with an interview.

The questionnaire will be delivered digitally via Google Forms for the ease of distribution, completion and analysis, and a structured questionnaire will be used. There will be a range of information that will need to be solicited from the teachers, so a mixed questionnaire consisting of both closed and open ended questions will be used. There will need to be some simple closed questions which can be measured quantitatively such as whether their school has made any changes regarding innovation and whether they consider their school innovative. The latter question will not be used exclusively, but will form a part of the pre-selection of schools to examine more closely as part of observational case studies.

There will be some questions which will require teachers to rate things on a scale. In particular, what they think the impact of innovation is, and to rate their school's level of innovation in chosen areas. The former is to determine whether innovation is something that is actually useful; up until this point there has almost been an assumption that it is a always a positive thing. The latter is to determine if there a prevailing 'type' of innovation that is more common than others in schools.

Respondents will be confidential but not anonymous. As there is a plan to select certain schools for further study, respondents' schools will be required in order to follow up, however their name is not required. 

While the aim of the questionnaires is to give a picture of the UAE that is as accurate as possible, the nature of the research is that it is not required for a statistically significant sample for the data to be usable. If there are only a handful of schools taking part, the data provided on those is sufficient to provide a narrative and discussion of what has taken place in those schools. If the research was to, for example, investigate a link between innovation and improvement in student performance then this would obviously not be the case. This will be seen further when investigating individual schools; the aim is not to draw conclusions about every school in the UAE, just to investigate what is taking place in some schools.
Despite that, the questionnaire target will be around 100 teachers. At a conservative estimate of five teachers in a school return rate, therefore 20 schools are required and 30 schools will be contacted at random.

One of areas with the potential to undermine the reliability and validity of data gathered during interviews is the phrasing of questions, specifically the use of leading questions. To this end, the interviews consisted of an introduction about the context of the research, followed by few, but open, general questions. Interviews were designed to be investigative rather then structured, so a complete list of questions was not suitable, but every interview revolved around questions such as: "what is innovation?", "what are your thoughts on innovation as an focus?", "is the school doing anything differently this year (in terms of innovation)?" and "what do you see in the future regarding the innovation focus?". The aim was to discover the thoughts and opinions of the leaders interviewed rather than to produce quantitative data, which is why open and general questions were used. 

These questions were then expanded on to provide some more quantitative data such as which areas they thought their school was innovative in and their role in the school. Qualitative data collection opportunities were included with questions allowing the respondent to expand on good and bad examples or innovation, both in and out of their school.
The final survey is included as Appendix \ref{appendix:teachersurvey}.

\subsubsection{Interviews}
As identified by Sharma et al., a portion of their framework relates to management and leadership. Interviews were chosen to discuss these aspects with senior managers to get a broader look at the range of innovation within the school, as well as the management and leadership focus, which only those higher up in the school would be able to discuss with confidence.

The interview process will happen after the questionnaires have been analysed, and will link in with the observations in that they will be selected from the schools chosen for the observations.

There is planned to be two or three members of staff interviewed at roughly three to five schools depending on availability. The people planned to be interviewed will depends on the school, but typically senior leaders, people in charge of teaching and learning or teachers otherwise involved in innovation projects.

As the interviews will be following on from the questionnaires, the interview questions will be have an structure with the topics and direction guided by interesting data to come from the questionnaires. The aim of the interviews is to get a more indepth view of how the school is working, and planning to work, in terms of innovation. As every school is different, the interview must be tailored to the school and be allowed to divergen into suitable areas if necessary. 

Interviews will be recorded via dictaphone and key points or ideas will be collected and written down as summaries of the discussion in that school. Unlike the questionnaires where the exact words are important, the outcome of the interviews is to find patters and areas of interest, both within each individual school but also across schools.

\subsubsection{Observations and Case Studies}  An important part of a pragmatic methodology is discovering the context in which research is taking place. Referring back to one of the reasons the pragmatic methodology was chosen, the idea of the research being iterated or built upon as it progressed is one that is seen in this data collection method. The case studies schools were not pre-selected, but were planned to be identified based on the response to the questionnaires. Whether or not schools were adapting the changes were an important part of the research, but finding good examples based on the questionnaires would be more useful as knowledge to be taken away from this research. Schools were to be identified by their employees as innovation, and a broad range of innovative practice was required to study in further detail. A 'thick description' "refers to the researcher’s task of both describing and interpreting observed social action (or behavior) within its particular context" \cite[p. 543]{thickdescription}. In order to discover the 'thick description' within schools, observational case studies were chosen to provide this

A 'thick description' "refers to the researcher’s task of both describing and interpreting observed social action (or behavior) within its particular context" \cite[p. 543]{thickdescription}. An important part of a pragmatic methodology is discovering the context in which research is taking place. In order to discover the 'thick description' within schools, observational case studies were chosen to provide this context.
Following on from the questionnaires, three to five schools will be selected to examine in more depth. The questionnaires give a snapshot of how teachers understand and view innovation and the interviews give a idea of how senior leaders and those in similar positions think about innovation and what their plans are. The purpose of the observations are to get an overview what is going on in the school across the whole school year. 

Within each school, a person who has previously responded to a questionnaire will be approached to become an observer, the only prerequisite is that they fully understand innovation in education and they are aware of the fact that ADEC has introduced this new focus. The observer in each school will be responsible for creation an observational case study on their school. The observational studies, also known as natural experiments \cite[p. 2]{0a338f}, will consist of the observers going about their normal daily lives and note down any references to innovation they come across, any projects that are announced or any plans related to innovation. The observation will run roughly for two terms to collect the results prior to the end of the year.

This extra layer of research on top of the questionnaires is yet again due to seeking the maximum context for the research. While a small amount of context can be given in questionnaires, there would not be enough for a 'thick description'. Case studies "can establish cause and effect, indeed one of their strengths is that they observe effects in real contexts, recognizing that context is a powerful determinant of both causes and effects" \cite[p. 181]{Cohen2005}.

The drawbacks of the case study is that it can be too localised or contextualised to be useful to be generalisable. The impact of this is planned to be mitigated by the fact it the good practice is aiming to be itself abstracted away to provide the most useful generalisation, as well as including this as a part of the greater mixed methodology.
